First Order Alternation

### 2019-02-03 quantifiers/body.tex
ok

Even for finite alphabets, complementation of finite-state automata
faces inherent exponential blowup, due to nondeterminism. However, if
we allow universal nondeterminism, in addition to the classical
existential nondeterminism, complementation is possible is linear
time. The automata having both existential and universal
nondeterminism are called \emph{alternating automata}
\cite{ChandraKozenStockmeyer81}. A finite-alphabet alternating
automaton is described by a set of transition rules $q \arrow{a}{}
\phi$, where $q$ is a state, $a$ is an input symbol and $\phi$ is a
boolean formula, whose propositional variables denote successor
states.

>>>>

Even for finite alphabets, complementation of finite-state automata
faces inherent exponential blowup, due to nondeterminism. However, if
we allow universal nondeterminism, in addition to the classical
existential nondeterminism, complementation is possible is linear
time. Having both existential and universal nondeterminism defines the
\emph{alternating automata} model \cite{ChandraKozenStockmeyer81}. A
finite-alphabet alternating automaton is described by a set of
transition rules $q \arrow{a}{} \phi$, where $q$ is a state, $a$ is an
input symbol and $\phi$ is a boolean formula, whose propositional
variables denote successor states.
